---
title: "Binomial"
author: "Max Sima"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial
The package `"binomial"` is a implement functions for calculating probabilities of a binomial random variable, given number of trials, number of success, and probabilities, and to visualize the binomial distribution, mean, variance and other relative calculations.

## Function bin_choose()
The first step is to get the binomial distribution is to use the function bin_choose(). The function bin_choose calculates the number of combinations in which k successes can occur in n trials.
Here are 3 samples of bin_choose()
```{r}
bin_choose(n = 5, k = 2)
bin_choose(5, 0)
bin_choose(5, 1:3)
```

## Function bin_probability()
You can use the function bin_probability to caluclate the probability given k successes in n trials.
Here are 3 samples of bin_probability()
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)
bin_probability(success = 55, trials = 100, prob = 0.45)
```

## Function bin_distribution()
You can use the function 'bin_distribution()' to get a data frame with the probability distribution: successes in the first column, probability in the second column.
Here is a sample of the bin_distribution()
```{r}
# binomial probability distribution
bin_distribution(trials = 5, prob = 0.5)
```

You can use the function 'plot()' to create the probability histogram of a binomial distribution object "bindis".
Here is a sample of the plot method
```{r}
# plotting binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

## Function bin_cumulative()
You can use the function 'bin_cumulative()' to get a data frame with both the probability distribution and the cumulative probabilities: successes in the first column, probability in the second column, and cumulative probabilities in the third column.
Here is a sample of bin_cumulative()
```{r}
# binomial cumulative distribution
bin_cumulative(trials = 5, prob = 0.5)
```

You can use the function 'plot()' to create the cumulative distribution in an object 'bincum'
Here is a sample of the plot method
```{r}
# plotting binomial cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```


## Function bin_variable()
You can use the functiona 'bin_variable()' to list with named elements:trials: number of trials and prob: probability of success
Here is a sample of bin_variable()
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
```

You can print 'summary.binvar' as following 
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```


## Functions of  measures 
You can use functions of  measure to get relative calculation of binomial, such as mean, variance, and mode etc.
Here are several samples of these function
```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```
